MS_Intro_Short

### 2022-04-19 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
added abstract

---
title: "MS_Intro_Short"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`

>>>>

---
title: "MS_Intro_Short"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
